Semi-supervised low-rank logistic regression for high-dimensional neuroimaging data

### 2015-05-30 paper_nips/paper.tex
Added explicit description of method to abstract

\documentclass{article} % For LaTeX2e
\usepackage{nips14submit_e,times}
\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath,amsfonts,amsthm}
\usepackage{bbm}
\usepackage{algorithm,algorithmic}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{bbm}
\usepackage[titletoc]{appendix}
\usepackage{wrapfig}
\usepackage{afterpage}
\usepackage{amssymb}
\usepackage{booktabs}

@@

@@

\begin{abstract}
Imaging neuroscience links human behavior to aspects of brain
biology in ever-increasing datasets.
%
Existing neuroimaging methods typically perform either discovery of unknown
neural structure or testing of neural structure associated with mental tasks.
%
However, testing hypotheses on the neural correlates of mental tasks
depends on the representation of the observations.
%
We therefore propose to optimize
representation and task classification in
an identical statistical learning problem.
%
We show that this approach yields more accurate and more interpretable
neural models of psychological tasks in a reference dataset.
%

>>>>

\documentclass{article} % For LaTeX2e
\usepackage{nips14submit_e,times}
\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath,amsfonts,amsthm}
\usepackage{bbm}
\usepackage{algorithm,algorithmic}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{bbm}
\usepackage[titletoc]{appendix}
\usepackage{wrapfig}
\usepackage{afterpage}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{ulem}

@@

\newcommand{\suggestadd}[1]{{\color{blue} #1}}
\newcommand{\suggestremove}[1]{{\color{red} \sout{#1}}}

@@

\begin{abstract}
Imaging neuroscience links human behavior to aspects of brain
biology in ever-increasing datasets.
%
Existing neuroimaging methods typically perform either discovery of unknown
neural structure or testing of neural structure associated with mental tasks.
%
However, testing hypotheses on the neural correlates of mental tasks
depends on the representation of the observations.
%
% XXX Michael: Added explicit outline of the model, description can be 
% XXX improved
We therefore propose to optimize
representation and task classification in
\suggestremove{an identical} \suggestadd{a unified} statistical learning 
problem\suggestadd{, by introducing a multinomial logistic regression with
joint rank constraint, which we regularize by forcing representational
capacity in the form of an autoencoder}.
%
We show that this approach yields more accurate and more interpretable
neural models of psychological tasks in a reference dataset.
%
